DRAFT_Cleaning

### 2024-12-09 Draft_Cleaning.Rmd
adjusted tuning params

tune_grid <- expand.grid(
  nrounds = c(50, 100, 150), 
  max_depth = c(3, 6, 9), 
  eta = c(0.1, 0.2, 0.3), 
  gamma = c(0, 0.1), 
  colsample_bytree = c(0.6, 0.8), 
  min_child_weight = c(1, 2, 5), 
  subsample = c(0.8, 1)
)

@@

fit_dredge2 = train(VOLUMEDREDGED ~ .,
                   data = gage_xgb,
                   method = "xgbTree",
                   tuneGrid = tune_grid,
                   verbosity = 0,
                   trControl = ctrl,
                   na.action = na.exclude)

>>>>

tune_grid <- expand.grid(
  nrounds = c(50, 100, 150), 
  max_depth = c(3, 6, 9), 
  eta = c(0.1, 0.2, 0.3), 
  gamma = 0, 
  colsample_bytree = 0.8, 
  min_child_weight =1, 
  subsample = c(0.8, 1)
)

@@

fit_dredge2 = train(VOLUMEDREDGED ~ .,
                   data = gage_xgb,
                   method = "xgbTree",
                   tuneGrid = tune_grid,
                   trControl = ctrl,
                   na.action = na.exclude)
